Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-25 paper/zhang-cook-laa-langrene-menendez.Rmd
code, gif and vimeo link for animated pca plot

```{r toy-pca-animated, fig.cap = "A selected number of frames from the animated PCA plot. With animation, it is easier to track the progression from the start to finish in each algorithm."}
```

>>>>

```{r toy-pca-animated, fig.cap = "A selected number of frames from the animated PCA plots. With animation, it is easier to track the progression of each optimiser from the start to finish. A full video of the aimation can be found at \\url{https://vimeo.com/user132007430/review/504242845/b73f37175a}"}
```

### 2021-01-25 paper/zhang-cook-laa-langrene-menendez.tex
code, gif and vimeo link for animated pca plot

\caption[A selected number of frames from the animated PCA plot]{A selected number of frames from the animated PCA plot. With animation, it is easier to track the progression from the start to finish in each algorithm.}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

@@

>>>>

\caption{A selected number of frames from the animated PCA plots. With animation, it is easier to track the progression of each optimiser from the start to finish. A full video of the aimation can be found at \url{https://vimeo.com/user132007430/review/504242845/b73f37175a}}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{Soutput}
#> Called from: explore_trace_interp(., color = method, iter = id, group = method)
#> debug: iter <- dplyr::enexpr(iter)
#> debug: color <- dplyr::enexpr(color)
#> debug: group <- dplyr::enexpr(group)
#> debug: if ("search_geodesic" %in% dt$method) {
#>     dt <- dt %>% clean_method()
#> }
#> debug: dt <- dt %>% clean_method()
#> debug: dt_interp <- get_interp(dt, group = !!group)
#> debug: interp_last <- dplyr::bind_rows(get_start(dt), get_interp_last(dt, 
#>     group = !!group))
#> debug: tick_x <- format_label(interp_last %>% dplyr::pull(!!iter), accuracy = accuracy_x)
#> debug: tick_y <- format_label(interp_last$index_val, accuracy = accuracy_y)
#> debug: a <- dt_interp %>% group_by(group = !!group) %>% dplyr::summarise(row = dplyr::n(), 
#>     diff = max(!!iter) - min(!!iter) + 1)
#> debug: if (!all(a$row == a$diff, TRUE)) {
#>     stop("there is gap(s) in the variable iter!")
#> }
#> debug: p <- dt_interp %>% ggplot2::ggplot(ggplot2::aes(x = !!iter, y = .data$index_val, 
#>     group = !!group)) + ggplot2::geom_line() + ggplot2::geom_point(data = interp_last, 
#>     ggplot2::aes(col = !!color), size = 3) + ggplot2::geom_vline(data = interp_last, 
#>     ggplot2::aes(xintercept = !!iter), lty = "dashed", alpha = 0.3) + 
#>     ggplot2::scale_x_continuous(breaks = tick_x) + ggplot2::scale_y_continuous(breaks = tick_y, 
#>     labels = scales::label_number(accuracy = accuracy_y)) + theme_fern() + 
#>     ggplot2::theme(legend.position = "none") + ggplot2::ylab("Index value") + 
#>     ggplot2::xlab("Time")
#> debug: if (nrow(dt_interp) < cutoff) {
#>     p <- p + ggplot2::geom_point(ggplot2::aes(x = !!iter, y = .data$index_val, 
#>         col = !!color))
#> }
#> debug: p
\end{Soutput}
\begin{widefigure}
